This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-03 article.tex
Small tweaks

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
To come at the exact weight of things= in the scientific steel-yard, the fulchrum, [Walter Shandy] would say, should be almost invisible, to avoid all friction from popular tenets=,---without this= the minutiae of philosophy, which should always= turn the balance, will have no weight at all---Knowledge, like matter, he would affirm, was= divisible in infinitum---that the grains= and scruples= were as= much a part of it, as= the gravitation of the whole world.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}}

@@

Where can we put a 5-byte DEFLATE header such that it won't corrupt
the PDF? We could use our standard trick of putting it in a PDF object
stream that we've exploited countless times before to enable
PoC$\|$GTFO polyglots. The trouble with that is: Object streams are
fixed-length, so once the PDF is decompressed (\textit{i.e.},~when a
repo is cloned from the git bundle), then all of the 5-byte DEFLATE
headers will disappear and the object stream lengths would all be
incorrect. Instead, I chose to use PDF comments, which start at any
occurrence of the percent sign character~(\%) outside a string or
stream and continue until the first occurrence of a newline.  All of
the PDF viewers I tested don't seem to care if comments include
non-ASCII characters; they seem to simply scan for a
newline. Therefore, we can inject ``\texttt{\%\textbackslash n}''
between PDF objects and move the DEFLATE headers there. The only
caveat is that the DEFLATE header itself can't contain a newline
byte~(\texttt{0x0A}), otherwise the comment would be ended
prematurely.  We can resolve that by adding extra spaces to the end of
the comment, increasing the length of the following DEFLATE block and
thus increasing the length bytes in the DEFLATE header and avoiding
the \texttt{0x0A}. The only concession made with this approach is that
PDF Xref offsets in the deflated version of the PDF will be off by a
multiple of 5, due to the removed DEFLATE headers. Fortunately, most
PDF readers can gracefully handle incorrect Xref offsets (at the
expense of a slower loading time), and this will only affect the PDF
contained in the repository, \emph{not} the PDF polyglot.

>>>>

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
To come at the exact weight of things= in the scientific steel-yard, the fulchrum, [Walter Shandy] would say, should be almost invisible, to avoid all friction from popular tenets=,---without this= the minuti\ae\ of philosophy, which should always= turn the balance, will have no weight at all---Knowledge, like matter, he would affirm, was= divisible in infinitum---that the grains= and scruples= were as= much a part of it, as= the gravitation of the whole world.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}}

@@

Where can we put a 5-byte DEFLATE header such that it won't corrupt
the PDF? We could use our standard trick of putting it in a PDF object
stream that we've exploited countless times before to enable
PoC$\|$GTFO polyglots. The trouble with that is: Object streams are
fixed-length, so once the PDF is decompressed (\textit{i.e.},~when a
repo is cloned from the git bundle), then all of the 5-byte DEFLATE
headers will disappear and the object stream lengths would all be
incorrect. Instead, I chose to use PDF comments, which start at any
occurrence of the percent sign character~(\%) outside a string or
stream and continue until the first occurrence of a newline.  All of
the PDF viewers I tested don't seem to care if comments include
non-ASCII characters; they seem to simply scan for a
newline. Therefore, we can inject ``\texttt{\%\textbackslash n}''
between PDF objects and move the DEFLATE headers there. The only
caveat is that the DEFLATE header itself can't contain a newline
byte~(\texttt{0x0A}), otherwise the comment would be ended
prematurely.  We can resolve that, if needed, by adding extra spaces
to the end of the comment, increasing the length of the following
DEFLATE block and thus increasing the length bytes in the DEFLATE
header and avoiding the \texttt{0x0A}. The only concession made with
this approach is that PDF Xref offsets in the deflated version of the
PDF will be off by a multiple of 5, due to the removed DEFLATE
headers. Fortunately, most PDF readers can gracefully handle incorrect
Xref offsets (at the expense of a slower loading time), and this will
only affect the PDF contained in the repository, \emph{not} the PDF
polyglot.
